---
title: "Links and Additional Resources"
---

```{r}
#| include: false
#| message: false
library(tidyverse)
```


This page contains links to additional resources for learning and using the tools and techniques related to MATH 463.

## Applied Math Resources

### Websites

### Readings

### Videos

## R Resources

### Websites

* [swirl](https://swirlstats.com/) - Learn R, in R.

### Readings

* [Introduction to Scientific Programming and Simulation Using R](https://nyu-cdsc.github.io/learningr/assets/simulation.pdf)

* [Hands-On Programming with R](https://rstudio-education.github.io/hopr/)

### Videos

*  Learn R in 39 minutes YouTube video, [watch video on YouTube](https://youtu.be/yZ0bV2Afkjc?si=EkmPjn5veIWGptY3).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="yZ0bV2Afkjc?si=EkmPjn5veIWGptY3",height=450) %>%
  vembedr::use_align("center")
```

*  R Programming Full Course for 2023 YouTube video, [watch the video on YouTube](https://www.youtube.com/live/Q5g6lYUn6Q4?si=Q3XZljkTGRrbACKP).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="Q5g6lYUn6Q4?si=Q3XZljkTGRrbACKP",height=450) %>%
  vembedr::use_align("center")
```

## Julia Resources

### Websites

### Readings

### Videos

*  Programming for Mathematicians with Julia (2023) YouTube video, [watch the video on YouTube](https://youtu.be/RWIMwqQFEPM?si=veR2KXfUeZlyMp3s).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="RWIMwqQFEPM?si=veR2KXfUeZlyMp3s",height=450) %>%
  vembedr::use_align("center")
```


*  Plotting in Julia YouTube video, [watch the video on YouTube](https://youtu.be/yZRw1uP41zI?si=99kK2vu8Adgv_YfH).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="yZRw1uP41zI?si=99kK2vu8Adgv_YfH",height=450) %>%
  vembedr::use_align("center")
```


*  Basic Linear Algebra with Julia YouTube video, [watch the video on YouTube](https://youtu.be/IFkQ0aB6eHs?si=aCXwqUZKeB8yLNGh).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="IFkQ0aB6eHs?si=aCXwqUZKeB8yLNGhs",height=450) %>%
  vembedr::use_align("center")
```


*  Intro to Differential Equations in Julia YouTube video, [watch the video on YouTube](https://youtu.be/lWmKCa6ih9Y?si=R_j8LMw1wg_YFI_p).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="lWmKCa6ih9Y?si=R_j8LMw1wg_YFI_p",height=450) %>%
  vembedr::use_align("center")
```


## Python Resources


### Websites

* [Numpy documentation page](https://numpy.org/).

* [Scipy documentation page](https://scipy.org/).

* [Matplotlib documentation page](https://matplotlib.org/).

* [Py-pde documentation page](https://py-pde.readthedocs.io/en/latest/getting_started.html).

### Readings

* [Getting started with python for science](https://scipy-lectures.org/intro/).

### Videos


*  Matplotlib Tutorial (Part 1): Creating and Customizing Our First Plots, [watch the video on YouTube](https://youtu.be/UO98lJQ3QGI?si=K_RhZhYrGPPoeTFF).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="UO98lJQ3QGI?si=K_RhZhYrGPPoeTFF",height=450) %>%
  vembedr::use_align("center")
```