---
title: "Links and Additional Resources"
---

```{r}
#| include: false
#| message: false
library(tidyverse)
```


This page contains links to additional resources for learning and using the tools and techniques related to MATH 463.

## Applied Math Resources

### Websites

### Readings

### Videos

## R Resources

### Websites

* [swirl](https://swirlstats.com/) - Learn R, in R.

### Readings

* [Introduction to Scientific Programming and Simulation Using R](https://nyu-cdsc.github.io/learningr/assets/simulation.pdf)

* [Hands-On Programming with R](https://rstudio-education.github.io/hopr/)

### Videos

*  Learn R in 39 minutes YouTube video, [watch video on YouTube](https://youtu.be/yZ0bV2Afkjc?si=EkmPjn5veIWGptY3).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="yZ0bV2Afkjc?si=EkmPjn5veIWGptY3",height=450) %>%
  vembedr::use_align("center")
```

*  R Programming Full Course for 2023 YouTube video, [watch the video on YouTube](https://www.youtube.com/live/Q5g6lYUn6Q4?si=Q3XZljkTGRrbACKP).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="Q5g6lYUn6Q4?si=Q3XZljkTGRrbACKP",height=450) %>%
  vembedr::use_align("center")
```

## Julia Resources

### Websites

### Readings

### Videos


## Python Resources


### Websites

### Readings

### Videos