---
title: "Homework Number"
author: "Your Name"
date: "`r Sys.Date()`"
format: 
  html:
    echo: true
    code-fold: true
    code-summary: "Show the code"
    toc: true
    toc-location: left
    self-contained: true
bibliography: bib_template.bib
---

```{r}
#| message: false
#| warning: false

# load essential packages
library(tidyverse) # for data manipulation and visualization
library(deSolve)     # for solving DEs

# set a default theme for ggplot2
theme_set(theme_bw())
```


## Exercise 1


### Part a

$$
\frac{dx}{dt} = ax; \quad x(0) = x_0
$$

To solve the differential equation, we can separate the variables (see for example, [@strogatz2015]):
$$
\frac{1}{x} dx = a dt
$$

Integrating both sides, we get:
$$
\int \frac{1}{x} dx = \int a dt
$$

This gives us:
$$
\ln|x| = at + C
$$

Exponentiating both sides, we have:
$$
|x| = e^{at + C} = e^C e^{at}
$$

Letting $e^C = K$, we can write:
$$
x = K e^{at}
$$

To find the constant $K$, we use the initial condition $x(0) = x_0$:
$$
x_0 = K e^{a \cdot 0} = K
$$

Thus, the solution to the differential equation is given by:

$$
x(t) = x_0 e^{at}
$$

### Part b

Here's a plot of a typical solution (when $a = 0.5$ and $x_0 = 2$):
```{r}
#| message: false
#| warning: false
#| label: fig-diff-eq-solution
#| fig.cap: "Plot of the solution to the differential equation $\\frac{dx}{dt} = ax$ with $a = 0.5$ and $x_0 = 2$."

# parameters
a <- 0.5
x0 <- 2
# time sequence
time <- seq(0, 10, by = 0.1)
# solution
x_t <- x0 * exp(a * time)
# create a data frame for plotting
df <- data.frame(time = time, x = x_t)
# plot
ggplot(df, aes(x = time, y = x)) +
  geom_line(color = "blue") +
  labs(title = "Solution of dx/dt = ax",
       x = "Time",
       y = "x(t)")
```


### Part c


## Exercise 2



...and so on...



# References


::: {#refs}
:::


:::{.callout-tip collapse="true"}
## Expand for Session Info
```{r}
#| echo: false


library(sessioninfo)
# save the session info as an object
pkg_sesh <- session_info(pkgs = "attached")
# print it out
pkg_sesh
```

:::